\thetitle

### 2020-11-11 writing/mutate.tex
format + prose tweaks

\begin{figure}
\begin{tabular}{p{2cm} | p{10cm} }
  {\bf  name} & {\bf description (author)}  \\

@@

\end{tabular}
  \caption{Benchmarks summary.}
  \label{table:benchmark-descriptions}
\end{figure}

@@

\begin{figure}
  \begin{tabular}{p{2.1cm} | p{5cm}  | p{5.5cm} }
    {\bf name} & {\bf description} & {\bf example} \\

@@

     \texttt{force-cond}
    & Replaces conditional test expressions with \texttt{\#t}.
    &  \begin{tabular}[t]{@{}l}
      \texttt{(if (= x 0) t e)} $\rightarrow$\\
      \texttt{(if \#t t e)}
    \end{tabular}\\
\hline
\end{tabular}
  \caption{Summary of mutators.}
  \label{table:mutation-ops}
\end{figure}

\subsection{Are these mutators good enough?}
\begin{itemize}
\item do these mutators work?
\begin{itemize}
\item now we need to see if these mutators actually produce interesting errors
\begin{itemize}
\item define interesting errors: type error + dynamic err w/ 3 modules on stack in a mixed configuration
\item this section will show if they do this on our benchmarks
\end{itemize}
\item do they actually produce interesting errors? -- for this need plot that's inverted version dyn-err-heatmap + total of mutants per benchmark
\item do we need all of the mutators?
\begin{itemize}
\item each one produces type errors + interesting scenarios
\item we conjecture they represent different kinds of mistakes
\end{itemize}
\end{itemize}
\end{itemize}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{./plots/mutant-breakdown}
  \caption{Interesting debugging scenarios produced by our mutators. Counts are cut off at 50.}
  \label{fig:mutant-breakdown}
\end{figure}

>>>>

\begin{figure*}
\begin{tabular}{p{2cm} | p{10cm} }
  {\bf  name} & {\bf description (author)}  \\

@@

\end{tabular}
  \caption{Benchmarks summary.}
  \label{table:benchmark-descriptions}
\end{figure*}

@@

\begin{figure*}
  \begin{tabular}{p{2.1cm} | p{5cm}  | p{5.5cm} }
    {\bf name} & {\bf description} & {\bf example} \\

@@

     \texttt{force-cond}
    & Replaces conditional test expressions with \texttt{\#t}.
    &  \begin{tabular}[t]{@{}l}
      \texttt{(if (= x 0) t e)} $\rightarrow$\\
      \texttt{(if \#t t e)}
    \end{tabular}\\
\hline
\end{tabular}
  \caption{Summary of mutators.}
  \label{table:mutation-ops}
\end{figure*}

\subsection{Are these mutators good enough?}

@@

\begin{figure*}
  \centering
  \includegraphics[scale=0.35]{./plots/mutant-breakdown}
  \caption{Interesting debugging scenarios produced by our mutators. Counts are cut off at 50.}
  \label{fig:mutant-breakdown}
\end{figure*}
